Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-02 Paper.tex
Add connection flow picture

In order to support the PoC a
Raspberry Pi 3 Model B (see figure 2) has been used
as a single board computer to provide a WiFi access point using
hostapd\cite{hostapd} daemon over Raspberry's WiFi chipset.
Raspberry Pi was also connected using ethernet cable
to an optical fiber commercial router.

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.2\textwidth]{images/rpi3modelb-sourceamazon.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 2. Raspberry Pi 3 Model B. Source: \cite{RaspberryPi3}
\\
\end{center}

@@

Dnsmasq\cite{dnsmasq} was used
as dynamic host configuration server for the wireless
network and
iptables\cite{iptables} was used as a firewall running
both inside the Raspberry; by default, iptables
was configured to
drop all packet
forwarding traffic from users connected to the wireless
domain and at the same time to redirect all
traffic to Raspberry's HTTP port where a
captive portal was listening incoming connections.

@@

>>>>

In order to support the PoC a
Raspberry Pi 3 Model B (see figure 2) has been used
as a single board computer to host all the required software.
Tested operative system was OSMC\cite{osmc} (a Debian based
GNU-Linux flavor) mainly used as media-center.
A WiFi access point using
hostapd\cite{hostapd} daemon over Raspberry's WiFi chipset.
Raspberry Pi was also connected using ethernet cable
to an optical fiber commercial router (\textit{see figure 2}).

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/physical-setup-y.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 2. Physical Setup.
\\
\end{center}

@@

Dnsmasq\cite{dnsmasq} was used
as dynamic host configuration server for the wireless
network users and
iptables\cite{iptables} was used as a firewall running
both inside the Raspberry; by default, iptables
was configured to
drop all packet
forwarding traffic from users connected to the wireless
domain and at the same time to redirect all
traffic to Raspberry's HTTP port where a
captive portal was listening incoming connections.

Main idea is that the users can join freely
to the wireless hotspot and access the web captive portal
(\textit{hosted on the same Raspberry}) application that
communicates with a back-end that controls iptables
rules and also an Infura light proxy able to relay RPC
calls arriving on 8545 port of the Raspberry.

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/con-flow-y.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 3. Physical Setup.
\\
\end{center}

@@

\bibitem{osmc} \href{https://osmc.tv/}{https://osmc.tv/}
